%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.grndlvl.com/}{\Large Jonathan DeLaigle}} & Email : \href{mailto:delaigle.jonathan@gmail.com}{delaigle.jonathan@gmail.com}\\
  \href{https://www.grndlvl.com/}{grndlvl.com} & Mobile : +1-706-589-6189 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Zivtech}{Philadelphia, PA}
      {Chief Technology Officer}{Aug 2020 - Present}
      \resumeItemListStart
        \resumeItem{Leadership}
          {Promoted from Director of Engineering to VP of Engineering, and then to Chief Technology Officer in 3 years. Lead and grow a distributed team of full-time engineers and contractors delivering high-profile client projects across React, React Native, PHP (Drupal), and WordPress stacks. Drive engineering best practices by establishing and enforcing protocols for updates, incident response, workflows, and code reviews.}
        \resumeItem{DevOps and System Administration}
          {Oversee infrastructure strategy, leveraging Docker and cloud hosting to ensure scalable and resilient deployments.}
        \resumeItem{Project Leadership}
          {Collaborate with stakeholders to align technical direction with business goals and client needs. Provide technical leadership and mentoring to senior engineers, fostering a culture of accountability and innovation. Oversee projects for healthcare and non-profit sectors, ensuring high standards of quality and performance.}
      \resumeItemListEnd

    \resumeSubheading
      {GollyGood Software}{Augusta, GA}
      {Senior Software Engineer \& Co-Founder}{Aug 2016 - Present}
      \resumeItemListStart
        \resumeItem{Staff augmentation}
          {Universal ``drop in place" engineer at various levels including technical leadership.}
        \resumeItem{DevOps}
          {Created systems deploy code using CircleCI, Pantheon, Jenkins, TravisCI, and Probo.CI}
        \resumeItem{Drupal}
          {Create training materials for Drupal8, migrate sites to Drupal8. Write integrations for Klaviyo, Amazon S3, LDAP, and PDFtk.}
      \resumeItemListEnd

    \resumeSubheading
      {Independent Consultant}{Augusta, GA}
      {Senior Software Engineer}{May 2014 - Aug 2016}
      \resumeItemListStart
        \resumeItem{Staff augmentation}
          {Universal ``drop in place" engineer at various levels including technical leadership.}
        \resumeItem{Requirements gathering}
          {Gathered requirements and created technical specifications with accurate estimates.}
        \resumeItem{DevOps}
          {Designed, developed, and maintained in house local development tools built on Vagrant and Chef.}
        \resumeItem{Security}
          {Maintained security updates for agency client websites.}
      \resumeItemListEnd

    \resumeSubheading
      {Mediacurrent}{Alpharetta, GA}
      {Senior Drupal Developer}{July 2013 - May 2014}
      \resumeItemListStart
        \resumeItem{Lead}
          {Led several high profile enterprise projects to success. Reviewed and instructed junior software engineers and interface specialists on code for standardization, security, performance and clarity.}
        \resumeItem{DevOps}
          {Designed, developed, and maintained in house local development tools built on Vagrant and Chef.}
        \resumeItem{Drupal, Joomla!, Wordpress}
          {Designed, developed, and maintained migrations, version release systems based on git, and mass refactoring of code bases for security, performance, and standardization.}
      \resumeItemListEnd

    \resumeSubheading
      {Advomatic}{New York, NY}
      {Web Developer}{Aug 2008 - Dec 2013}
%      \resumeItemListStart
%        \resumeItem{Lead}
%          {Led several high profile enterprise projects to success by gathering requirements and estimating accurately. Reviewed and instructed junior software engineers and interface specialists on code for standardization, security, performance and clarity. Provided 2$^{nd}$ tier support for all business units, provided documentation, and trained staff.}
%        \resumeItem{Area Expert}
%          {Acting in house expert on mobile, SOAP, REST, and single sign on solutions.}
%      \resumeItemListEnd

%    \resumeSubheading
%      {Morris DigitalWorks}{Augusta, GA}
%      {Associate Web Developer, Intern}{July 2006 - Aug 2008}
%      \resumeItemListStart
%        \resumeItem{Lead}
%          {Led several medium-sized projects with 1-2 members to success, provided 2$^{nd}$ tier support for all business units, provided documentation, and trained staff.}
%        \resumeItem{Develop}
%          {Developed, designed, maintained migration solutions, Drupal, and user interfaces in HTML and Flash for large magazines, radio, and newspaper websites.}
%        \resumeItem{Systems}
%          {Assisted system engineers with configuring and maintaining LAMP environments.}
%      \resumeItemListEnd

  \resumeSubHeadingListEnd

%\section{Projects}
  %\resumeSubHeadingListStart
    %\resumeSubItem{QuantSoftware Toolkit}
      %{Open source python library for financial data analysis and machine learning for finance.}
    %\resumeSubItem{Github Visualization}
      %{Data Visualization of Git Log data using D3 to analyze project trends over time.}
    %\resumeSubItem{Recommendation System}
      %{Music and Movie recommender systems using collaborative filtering on public datasets.}
    %\resumeSubItem{Mac Setup}
      %{Book that gives step by step instructions on setting up developer environment on Mac OS.}
  %\resumeSubHeadingListEnd

\section{Technical Skills}

\resumeSubHeadingListStart
  \resumeSubItem{Tools}{Android SDK, Apache, Docker, Docker Compose, Drupal, jQuery, Kubernetes, Latex, MariaDB, MySQL, REST, Git, SOAP, Symfony, Vim, Wordpress}
  \resumeSubItem{Cloud Platforms}{Acquia, Akamai(Linode), AWS, Digital Ocean, Google Cloud, Pantheon.io, Platform.sh, Upsun}
  \resumeSubItem{Languages}{Bash, C\#, C++, Haskell, HTML5, CSS3, JavaScript, Java, Perl, PHP, Python, Ruby, UML, XML, XHTML, XPATH}
\resumeSubHeadingListEnd

%\section{Volunteer}
%
%\resumeSubHeadingListStart
%
%  \resumeSubheading
%    {Drupal contributor}{}
%    {Community member}{Oct 2009 - Present}
%    \resumeItemListStart
%      \resumeItem{Development}{Maintain several modules, contribute patches to modules and core.}
%    \resumeItemListEnd
%
%\resumeSubHeadingListEnd

%
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Augusta University}{Augusta, GA}
      {Bachelor of Science in Computer Science;  GPA: Cum Laude}{Aug 2007 -- May 2018}
    \resumeSubheading
      {Augusta University}{Augusta, GA}
      {Certificate in Cyber Defender}{Jan 2018 -- May 2018}
    \resumeSubheading
      {Augusta Technical College}{Augusta, GA}
      {Associate of Applied Science in Computer Programming}{Aug 2004 -- May 2007}
  \resumeSubHeadingListEnd

\end{document}
